Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_wrapping.tex
changed ebay reference to footnote
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@863 d8b0c59b-6544-0410-94d9-83a5658a058e

In the top input field of Figure ~\ref{fig:construct_service_request}, the user may drop an example http request taken e.g. form the service documentation e.g. from \cite{eBayShoppingAPIs}. The tool analyses the example request and in the middle of the screen a form for editing the request parameters is provided. In our example, the user has connected the \textit{QueryKeywords} parameter with the input parameter \textit{search\_key} by adding a corresponding reference to the value field of that parameter. In addition, we have retrieved an access key which has been entered as value for the \textit{appid} parameter.

>>>>

In the top input field of Figure ~\ref{fig:construct_service_request}, the user may drop an example HTTP request taken e.g. form the service documentation e.g. from its website\footnote{http://developer.ebay.com/products/shopping/}. The tool analyses the example request and in the middle of the screen a form for editing the request parameters is provided. In our example, the user has connected the \textit{QueryKeywords} parameter with the input parameter \textit{search\_key} by adding a corresponding reference to the value field of that parameter. In addition, we have retrieved an access key which has been entered as value for the \textit{appid} parameter.
